### 2012-12-03 inst/examples/policycosts/quick_examples.Rmd
running code for policy costs: Figure 3 using fixed rather than algorithmic values for coefficients, taken to match http://www.carlboettiger.info/2012/11/27/polict-costs-work.html

```{r graphing-options, include=FALSE}
#opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor=element_line(colour="transparent"))
theme_set(theme_notebook)
```

``` {r  parallel}
require(snowfall)
sfInit(cpu=16, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

@@

## Apples to Apples levels

### Loop over penalty functions and magnitudes

``` {r  bigloop, dependson=c("setup", "reed", "fees")}
policies <- 
sfSapply(penaltyfns, function(penalty){
  policies <- 
  sapply(c2, function(c2){
      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = penalty(c2))
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) 
  })
})
````

Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

Quadratic costs on fishing effort have to be done separately,

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1*c2*h/x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.

``` {r npv-plot, dependson="quadcosts"}
npv0 <- dat[1,3] 
npv0
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:

```{r apples_plot, dependson="quadcosts"}
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

@@

# Plots

``` {r p0, dependson="tidy"}
p0 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1) +
  geom_line(aes(time, harvest, col=penalty_fn, lty=penalty_fn))+ 
  labs(x="time", y="stock size", title = "Stock Dynamics")
```

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
```

```{r p2, dependson="tidy", fig.width=12}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
````

>>>>

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor=element_line(colour="transparent"))
theme_set(theme_notebook)
```

``` {r}
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
```

@@

```{r apples}
apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
xtable(apples)
````

@@

## Plots

``` {r p0, dependson="tidy"}
p0 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1) +
  geom_line(aes(time, harvest, col=penalty_fn, lty=penalty_fn))+ 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p0
```

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r p2, dependson="tidy", fig.width=12}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````
